%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Project Manager} % Job title
    {Aeon Cloud} % Organization
    {Shanghai, China} % Location
    {May. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Conducted feasibility analysis with customers and managed requirements.
        \item Organized regular meetings with customers to address development issues. 
        \item Managed project schedules and risks.
        \item {Constructed application infrastructure including web (Ant Design Vue), server (microservices), and mobile (Flutter)}.
        \item Designed relational database tables derived from business domain transitions
        \item Participated in coding and testing
        \item {Documented software development activities, API interface, and test cases}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {Senior Project Manager} % Job title
    {Yinma Technology} % Organization
    %{Portland, U.S \& Beijing, PRC} % Location
    {Shanghai, China} % Location %Note: only for H1B
    {Sep.2019 - Mar.2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led software development team to accomplish the company missions.}
        \item {Defined KPIs for the development team and conducted assessments.}
        \item {Oversaw the development of a dental clinic information system.}
        \item {Defined and refined requirements with the product department.}
        \item {Reviewed and optimized code, seeking better solutions with team members}
        \item {Guided team members to achieve their goals}
        \item \textbf{Participate in coding and testing of critical modules}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer \& Consultant} % Job title
    {Yizit} % Organization
    {Shanghai, PRC} % Location
    {Jul. 2016 – Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a senior software engineer. \\ - Led the development of multiple projects for the automobile industry, such as MES, WMS, MRO, ANDON, APS.  \\ - Continuous software integration \& release and drove software development activities to guarantee project moving forward smoothly. \\- Delved into code to drive critical issue debugging and improved system stability and performance to meet complex user’s environment. \\ - Established software configuration and maintenance flows, project management systems, and issue tracking systems.  \\ - \textbf{Participate in coding and testing of critical modules}}
        \item {As a software development consultant. \\ - Provided the suggestions on the feasibility for projects in demonstration phase\\- Evaluated software architecture for functionality, performance, maintainability, security, cost, and compliance.\\- Solved severe problems in delivered software projects}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
