%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Build a business platform between merchants and residents within a community.} % summary
    {Residential Community Information  Platform} % Title
    {Aeon Cloud, Shanghai, China} % Location
    {Apr.2020 - Oct.2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item { \textit{Key Contributes}:\\-Defined business entities and aggregate boundaries, designed coding pedestal, installed and maintained infrastructure applications  }
        \item { \textit{Challenges and Solutions}: \\-Ensured system fault tolerance and consistency using CP in the CAP theorem and utilized a business cluster strategy for availability. \\-Resolved distributed transaction consistency with Apache Seata. \\-API response time is within 100 milliseconds.}
        \item {\textit{Results and Impacts}: \\- Helped users find lost pets and reduced waste of idle items  }
        \item {\textit{Technologies Used}: \\- Components:Spring Boot, Spring Cloud, Mybatis, Shiro, AxonFramework(\textbf{DDD}), Restfull, MVC, Log4j, jackson, lombok, OpenApi \\- {Microservices: \textbf{Service Discovery}: { Nacos/ZooKeeper/Eureka/Apollo,} \textbf{Config Server}: Spring Cloud Vault, Spring Cloud Config, Nacos,  \textbf{Api Gateway}: OpenFeign  \textbf{Distribution Tracing}: Spring Cloud Sleuth/Zipkin, \textbf{Circuit Breakers}: Hystrix, Sentinel} \\-DDD: AxonFramework  \\-Infrastructures: RabbitMQ, Minio, Zookeeper, Redis Server, Jekinks, MySQL, Docker\&Docker Compose, Vault/Nacos }
        % \item {\textit{Role}: Project Leader}  
        % \item {\textit{Codes}: \\- \hyperlink{https://gitee.com/adx-common}{https://gitee.com/adx-common}  \\- https://gitee.com/adx-domain}
      \end{cvitems}
    }

  % \cventry
  % {Build a self-hosting of real-time broadcasting}
  % {Self-hosting Ants Broadcasting System}
  % {Shanghai, China} 
  % {Ja.}
  % {
  %   \begin{cvitems}
  %       \item {\textit{Key Contributes}: Configured Cisco VLAN for xxxx
  %       }
  %       \item {\textit{Challenges and Solutions}: 
  %       }
  %       \item {\textit{Results}}
  %   \end{cvitems}
  % }
%---------------------------------------------------------
  \cventry
    {Build a software infrastructure for maintaining the WTPIS} % summary
    {Disney Water Treatemnt Plant Information System  (WTPIS)} % Title
    %{Brook Haven, U.S} % Location
    {Aeon Cloud, Shanghai, China} % Location % only for H1B
    {Jan.2023 - June.2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {\textit{Key Contributes}: \\
        -Developed RESTful APIs with C\#  to manage device listings, user authentication, and work order processing and so on. 
        \\-Integrated MySQL for efficient data storage and retrieval, optimizing database queries for better performance}
        \\ -Designed and implemented the front-end using AntDesign Vue, ensuring a responsive and user-friendly interface. 
        \item {\textit{Challenges and Solutions}: \\-Faced performance issues with database queries and resolved them by indexing key fields and optimizing query logic }
        \item {\textit{Results and Impacts}: \\-Successfully launched the application \\-The response time of problem handling was reduced by 20\% within the first three months.}
        \item {\textit{Technologies Used}: \\ -Server: MySQL, Linq, MongoDB, MVC,  Autofac, Castle, Quartz, Minio, Redis, Mongo, Log4Net etc. \\-Web: AntDesign Vue, Node.js, socket.io-client, pdf, i18n, echarts, axios etc. \\-Flutter:bloc, cached\_network\_image, video\_player, cached\_pdf\_view, loading\_indicator, intl, etc. \\ -Documentation: OpenApi}        
        % \item {\textit{Role}: Lead Developer}
        % \item {\textit{}{Codes:} \\- https://gitee.com/tjush/wtp-web.git \\- https://gitee.com/tjush/wtp-api.git \\- https://gitee.com/tjush/wtp-mobile.git}
      \end{cvitems}
    }
    %---------------------------------------------------------
  \cventry
    {a comprehensive platform for streamlining the management and operational processes of dental clinics} % summary
    {Dentist information system({DCIS})} % Title
    {Yinma, Shanghai, China} % Location
    {Sept.2019 - Dec.2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {\textit{Key Contributes}:  \\-Participated in the definition of all business work processes. \\-Orchestrated all business flowcharts and nodes using camunda-modeler \\-Designed the common framework of the program based on workflow processing within Camunda}
        \item {\textit{Challenges and Solutions}: \\- In order to facilitate the development based on the Camunda workflow engine, a new architecture needs to be designed}
        \item {\textit{Results and Impacts}: \\-Saved about 30\% of the time from appointment to  consultation. \\-Patients can check the doctor's orders on the APP and confirm the execution status of each item in the order.}
        \item {\textit{Technologies Used}: Camunda, xxl-job, Spring Boot, }
        % \item {\textit{Role}: Project Leader}
      \end{cvitems}
    }




%---------------------------------------------------------
\end{cventries}
